Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2017-07-06 workflow/workflow.Rmd
update todo list

- try running workflow with more genes (DR),
- install and run package making sure we can build the vignette using R 3.4 and bioc-devel 3.6 (all?),
- make singlecellworkflow package public (FP).]

[FP: todo after converting to latex (FP):

- add space between paragraphs, 
- check uniformity first/last names in references, 
- add back space after word task in abstract, 
- submit.]

>>>>

- try running workflow with more genes (DR if time),
- colors and labels in plotBarplot to compare original and our clustering (EP, DR),
- check removal cluster c4 (all)
- make singlecellworkflow package public (FP).]

[FP: todo after converting to latex (FP): 
- submit.]
